---
title: 'bootcamp assesment # 10'
author: "Ed Harris"
date: "2022-06-15"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<br>
 
## Question 10

Create a github repository called `bootcamp`, create an html R Markdown document with your complete answer to question #9 in it, showing both code and graph output, and push your R markdown file, your html file and related files to your new repository.  Your answer to this question should simply be a commented html link to your new github repository.  

<br>
 
## Data and ANOVA 
```{r InsectSprays}
data(InsectSprays)
anova(lm(InsectSprays$count ~ InsectSprays$spray))
```


There is a strong overall difference in mean insect count between different spray treatments (ANOVA: F 5,66 = 34.7, P < 0.0001).

<br>
 
## Boxplot



```{r pressure, echo=T}
boxplot(InsectSprays$count ~ InsectSprays$spray,
        xlab = 'Spray treatment',
        ylab = 'Insect count',
        col = colors()[1:6],
        cex.lab=1.5,
        cex.axis = 1.2)
```

